Learning CNN filters from user-drawn image makers for coconut-tree image classification

### 2020-06-12 main.tex
Updates from Overleaf

In order to assess the impact of FLIM in reducing the need for annotated samples, we randomly select 100 regions from each class for training and left the remaining 11387 regions for testing. We have also repeated this procedure three times in order to compute mean and standard deviation of the results in precision, recall, and f-score. By vectorizing and projecting on 2D~\cite{maaten2008visualizing} the 200 training images of each split, the user identified cohesive groups of images from each class and selected two representative images from each class to draw markers. We have neither evaluated markers from a higher number of images nor multiple network architectures trained by FLIM. We just projected the simplest network with a single convolutional layer with weights obtained by FLIM from markers drawn in four images only.

several architectures based on FLIM and

analyzing the 2D t-SNE projection of the 200 training images, , the user selected

>>>>

In order to assess the impact of FLIM in reducing the need for annotated samples, we randomly selected 100 regions from each class for training and left the remaining 11387 regions for testing. We also repeated this procedure three times in order to compute mean and standard deviation of the results in precision, recall, and f-score. By vectorizing and projecting the 200 training images of each split on 2D~\cite{maaten2008visualizing}, the user identified cohesive groups of images from each class and selected two representative images from each class to draw markers. We neither evaluated markers from a higher number of images nor multiple network architectures trained by FLIM. We just trained by FLIM the simplest network with a single convolutional layer from markers drawn in four images only.
